Forecasting the old-age dependency ratio to determine the best pension age

### 2020-09-10 PensionAge.Rmd
Update based on Hanlin's email comments

@@

The model proposed by @HU07 is as follows:
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
\end{align}
Equation \eqref{eq:HU_1} describes the smoothing process. $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14]. $\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ is independent and identically distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score. It describes the dynamics of $s_t(x)$ over time. The $\phi_j(x)$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\beta_{t,j}$ for every $j$ is a time-varying index. The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation. The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$. The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively. In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
$$
  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
$$
We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.

@@

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models'}
autoplot(fertf)
```

>>>>

\todo[inline]{Adjust numbers in abstract as per Figure 9}

@@

The model proposed by @HU07 is as follows:
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
\end{align}
Equation \eqref{eq:HU_1} describes the smoothing process. $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14]. $\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ is independent and identically distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score. It describes the dynamics of $s_t(x)$ over time. The $\phi_j(x)$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\beta_{t,j}$ for every $j$ is a time-varying index. The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation. The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$. The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j^{th}$ principal component and scores of $s_t(x)-\mu(x)$ respectively. In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
$$
  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
$$
We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.

\todo[inline]{Add comment on choosing $J$}

@@

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models', message=FALSE}
autoplot(fertf)
```
